Notes on scheduling the SAA2019 meeting

### 2017-11-03 analysis/paper/saa2018_nonposter_sessions_while_loop.Rmd
csv for visual sched of nonposter sessions

@@

>>>>

# make a spreadsheet that looks like this plot

library(tidyr)
visual_schedule_plot_as_spreadsheet <- 
  x %>% 
  select(day_part_from_while.y, 
         sessions_for_plot, 
         computed_slot) %>% 
  distinct(sessions_for_plot, 
           .keep_all = TRUE) %>% 
  spread(day_part_from_while.y, 
         sessions_for_plot, 
         fill = "")

write_csv(visual_schedule_plot_as_spreadsheet,
          "../data/derived_data/visual_schedule_plot_as_spreadsheet.csv")

@@

- Many sessions of the same topic are put in the same day-part, which is undesirable. We may want to consider changing the while-loop to fill each day-part with one session per day-part, rather than filling a day-part, then moving to the next day-part, etc.
